Enriching Object Detection with 2D-3D Registration\\and Continuous Viewpoint Estimation

### 2015-04-01 2349.tex

\author{Christopher B. Choy, Michael Stark, Sam Corbett-Davies, Silvio Savarese\\
    Stanford University, Max Plank Institutes\\
    {\tt\small \{chrischoy, scorbett, stark, ssilvio\}@stanford.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
A large body of recent work on object detection has focused on exploiting 3D CAD
model databases to improve detection performance. Many of these approaches work
by aligning exact 3D models to images using templates generated from renderings
of the 3D models at a finite set of discrete viewpoints. The training procedures
for these approaches, however, are very expensive and require gigabytes of
memory and storage, and the viewpoint discretization hampers pose estimation
performance.

We propose an efficient method for synthesizing templates from 3D models that
runs on the fly -- that is, it quickly produces detectors for an arbitrary
viewpoint of a 3D model without expensive dataset-dependent training or template
storage. Given a 3D model and an arbitrary continuous detection viewpoint, our
method synthesizes a discriminative template by extracting features from a
rendered view of the object and decorrelating spatial dependences among the
features. Our decorrelation procedure relies on a gradient-based algorithm that
is more numerically stable than standard decomposition-based procedures, and we
efficiently search for candidate detections by computing FFT-based template
convolutions. Due to the speed of our template synthesis procedure, we are able
to perform joint optimization on scale, translation, continuous rotation, and
focal length. We provide an efficient GPU implementation of our algorithm, and
we validate its performance on 3D Object Classes and PASCAL3D+ datasets.

>>>>

\author{Christopher Bongsoo Choy\textsuperscript{\dag}, Michael Stark\textsuperscript{\dag \ddag}, Sam Corbett-Davies\textsuperscript{\dag}, Silvio Savarese\textsuperscript{\dag}\\
    \textsuperscript{\dag}Stanford University, \textsuperscript{\ddag}Max Plank Institutes\\
    {\tt\small \{chrischoy, scorbett, stark, ssilvio\}@stanford.edu}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
A large body of recent work on object detection has focused on exploiting 3D CAD
model databases to improve detection performance. Many of these approaches work
by aligning exact 3D models to images using templates generated from renderings
of the 3D models at a set of discrete viewpoints. However, the training
procedures for these approaches are computationally expensive and require
gigabytes of memory and storage, while the viewpoint discretization hampers
pose estimation performance.

We propose an efficient method for synthesizing templates from 3D models that
runs on the fly -- that is, it quickly produces detectors for an arbitrary
viewpoint of a 3D model without expensive dataset-dependent training or template
storage. Given a 3D model and an arbitrary continuous detection viewpoint, our
method synthesizes a discriminative template by extracting features from a
rendered view of the object and decorrelating spatial dependences among the
features. Our decorrelation procedure relies on a gradient-based algorithm that
is more numerically stable than standard decomposition-based procedures, and we
efficiently search for candidate detections by computing FFT-based template
convolutions. Due to the speed of our template synthesis procedure, we are able
to perform joint optimization of scale, translation, continuous rotation, and
focal length. We provide an efficient GPU implementation of our algorithm, and
we validate its performance on 3D Object Classes and PASCAL3D+ datasets.

### 2015-04-01 approach.tex

We report the real time analysis of whitening using decomposition and
Conjugate Gradient methods in Fig.~\ref{fig:whotime}. (a) compares the
absolute runtime of the different methods while (b) gives the obtained
speedup. We see that % We compare the speed of each of template generation methods in
% Fig.~\cite{fig:covariancetime_crop} Using naive Cholesky decomposition,
whitening the WHO template takes several seconds for realistic template sizes of
several hundred cells, but only 60ms using the Conjugate Gradient
method. If we use NZ-WHO, we can gain extra speed
up since we only whiten non-zero cells.

>>>>

We report the real time analysis of whitening using decomposition and
Conjugate Gradient methods in Fig.~\ref{fig:whotime}. (a) compares the
absolute runtime of the different methods while (b) gives the obtained
speedup. We see that % We compare the speed of each of template generation methods in
% Fig.~\cite{fig:covariancetime_crop} Using naive Cholesky decomposition,
whitening the HOG template takes several seconds for realistic template sizes of
several hundred cells, but only 60ms using the Conjugate Gradient
method. If we use NZ-WHO, we can gain extra speed
up since we only whiten non-zero cells.

### 2015-04-01 intro.tex

In this paper, we propose a novel method for 2D-3D alignment of
exemplar CAD models to real-world images that circumvents the need for
calibration, and greatly enhances the scalability of WHO. As a
result, we can render novel views and train corresponding exemplar
models {\em on the fly}, without the need for offline processing. We call these NZ-WHO templates \ref{fig:front}. As a
by-product, we can formulate the alignment problem as a parameter
search in a continuous pose space, consisting of yaw, pitch and roll, which
we implement using MCMC sampling.

@@

First, we present a novel method for training exemplar models from
rendered 3D CAD data {\em on the fly}, enabled by a novel variant of
WHO, termed NZ-WHO, and making efficient use of the specific
characteristics of rendered images. To our knowledge, our method
constitutes the first attempt to simultaneously render and train
exemplar detectors on the fly.
% In our paper, we present Non-Zero Whiten Histograms of Orientations
% (NZ-WHO) to dramatically speed up the template generation and get rid
% of time consuming calibration and yet achieves performance on par with
% calibrated templates. First, we will present NZ-WHO is more
% discriminative than WHO and introduce Conjugate Gradient method to
% speed up the whitening and create a high resolution template in just
% 80 milliseconds. Also, using this fast NZ-WHO template generation, we
% present \textbf{on-the-fly} template generation to fine tune an
% initial pose estimation to continuously refine translation, viewpoints
% (yaw, roll, pitch) and focal length.
%
Second, we demonstrate that our method can enrich the output of an existing object class
detector, such as the DPM~\cite{Felzenszwalb10} or the
R-CNN~\cite{Girshick14} with additional 3D information. By applying our
method to candidate detections provided by the respective detector, we can augment the original detections with an
estimate of 3D continuous pose and a 3D CAD model exemplar.
%
Finally, we give an in-depth experimental study that demonstrates
the effectiveness of our approach on a standard benchmark for
object detection and viewpoint estimation~\cite{Xiang14}.

>>>>

In this paper, we propose a novel method for 2D-3D alignment of
exemplar CAD models to real-world images that circumvents the need for
calibration, and greatly enhances the scalability of WHO. As a
result, we can render novel views and train corresponding exemplar
models {\em on the fly}, without the need for offline processing. We call these Non-Zero Whiten Histograms of Orientations(NZ-WHO) templates \ref{fig:front}. As a
by-product, we can formulate the alignment problem as a parameter
search in a continuous pose space, consisting of yaw, pitch and roll, which
we implement using MCMC sampling.

@@

First, we present a novel method for training exemplar models from
rendered 3D CAD data {\em on the fly}, enabled by a novel variant of
WHO, termed Non-Zero Whiten Histograms of Orientations(NZ-WHO), and making efficient use of the specific
characteristics of rendered images. To our knowledge, our method
constitutes the first attempt to simultaneously render and train
exemplar detectors on the fly.
% In our paper, we present Non-Zero Whiten Histograms of Orientations
% (NZ-WHO) to dramatically speed up the template generation and get rid
% of time consuming calibration and yet achieves performance on par with
% calibrated templates. First, we will present NZ-WHO is more
% discriminative than WHO and introduce Conjugate Gradient method to
% speed up the whitening and create a high resolution template in just
% 80 milliseconds. Also, using this fast NZ-WHO template generation, we
% present \textbf{on-the-fly} template generation to fine tune an
% initial pose estimation to continuously refine translation, viewpoints
% (yaw, roll, pitch) and focal length.
%
Second, we demonstrate that our method can enrich the output of an existing object class
detector, such as the DPM~\cite{Felzenszwalb10} or the
R-CNN~\cite{Girshick14} with additional 3D information. By applying our
method to candidate detections provided by the respective detector, we can augment the original detections with an
estimate of 3D continuous pose and a 3D CAD model exemplar.
%
Finally, we give an in-depth experimental study that demonstrates
the effectiveness of our approach on a standard benchmark for
object detection and viewpoint estimation~\cite{Xiang14}.
